
\begin{thebibliography}{3}
%========================================================
\bibitem{Graphene}
K.S.Novoselov A.K.Geim S.V.Morozov D.Jiang Y.Zhang S.V.Dubonos S.V.Grigorieva A. A.Firsov Electric Field Effect in AtomicallyThin Carbon Films // Science Vol 306, Issue 5696, 22 Oct 2004 .
\bibitem{semiconducter} C. H. Chen, W. Fabian, F. C. Brown, K. C. Woo, B. Davies, B. DeLong, and A. H. Thompson
Angle-resolved photoemission studies of the band structure of TiSe$_{2}$ and TiS$_{2}$ // Phys. Rev. B 21, 615 – Published 15 January 1980.
\bibitem{semimetal} F.R. Shepherd, P.M. Williams Photoemission studies of the band structures of transition metal dichalcogenides. I. Groups IVA and IVB. //Journal of Physics C: Solid State Physics, 7 (23). 4416-4426.
\bibitem{semimetal_or_semiconducter} Han Wang, Zhizhan Qiu, Weiyi Xia, Chen Ming, Yuyan Han, Liang Cao, Jiong Lu, Peihong Zhang, Shengbai Zhang, Hai Xu, and Yi-Yang Sun Semimetal or Semiconductor: The Nature of High Intrinsic Electrical Conductivity in TiS2 // The Journal of Physical Chemistry Letters 2019 10 (22), 6996-7001.
\bibitem{nanotube} Jun Chen, Suo-Long Li, Zhan-Liang Taoa and Feng Gaoa Low-temperature synthesis of titanium disulfidenanotubes //  Chemical communication Issue 8, 2003.
\bibitem{nanotube2} J. Chen, Z.L. Tho, S.L. Li. // Angew. Chemie-Intern. Edit., 42, 2147, 2003.
\bibitem{nanotube3} J. Chen, S.L. Li. Z.L. Tao, Y. Shen, C.X. Cui. // J. Amer. Chem. Soc., 125, 5284c, 2003.
\bibitem{nanotube4} Gotthard Seifert, Humberto Terrones, Mauricio Terrones, Gerd Jungnickel, and Thomas Frauenheim Structure and Electronic Properties of MoS 2 Nanotubes // Phys. Rev. Lett. 85, 146 – Published 3 July 2000
\bibitem{nanotube5} Humberto Terrones and Mauricio Terrones Curved nanostructured materials // New J. Phys. 5 126, 2003.
\bibitem{nanotube6} G. Seifert, H. Terrones, M. Terrones, S. Jungnickel, T. Frauenheim On the electronic structure of WS2 nanotubes //  Sol. St. Commun., 114, 245, 2000.
\bibitem{PhysRevB29}D. K. G. de Boer et al., Phys. Rev. B 29, 6797 (1984).
\bibitem{PhysRevB54}R. Claessen et al., Phys. Rev. B 54, 2453 (1996).
\bibitem{PhysRevB16}A. Zunger and A. J. Freeman, Phys. Rev. B 16, 906 (1977).
\bibitem{PhysRevB21}C. H. Chen et al., Phys. Rev. B 21, 615 (1980).
\bibitem{PhysRevB17}A. Zunger and A. J. Freeman, Phys. Rev. B 17, 1839 (1978).
\bibitem{PhysRevL55}O. Anderson, R. Manzke, and M. Skibowski, Phys. Rev. Lett. 55, 2188 (1985).
\bibitem{SolidStateCommun53}O. Anderson, G. Karschnick, R. Manzke, and M. Skibowski, Solid State Commun. 53, 339 (1985).
\bibitem{PhysRevB61}Th. Pillo et al., Phys. Rev. B 61, 16 213 (2000).
\bibitem{PhysRev65}K. Rossnagel, L. Kipp, and M. Skibowski, Phys. Rev. B 65, 235101 (2002).
\bibitem{PhyRevLet88} T. E. Kidd, T. Miller, M. Y. Chou, and T.-C. Chiang, Phys. Rev. Lett. 88, 226402 (2002).
\bibitem{TiTe2_1}de Boer, D. K. G. et al. Titanium ditelluride: Band structure, photoemission, and electrical and magnetic properties. Phys. Rev. B 29, 6797 (1984).
\bibitem{TiTe2_2} Arnaud, Y. Chevreton, M. Etude comparative des composés TiX 2(X=S, Se, Te). Structures de TiTe 2 et TiSeTe. J. Solid State Chem. 39, 230 (1981).
\bibitem{TiTe2_3} Koike, Y., Okamura, M., Nakanomyo, T. Fukase, T. Log T Dependence of Resistivity and Negative Magnetoresistance in the Layered Compound TiTe2 . J. Phys. Soc. Jpn 52, 597 (1983).
\bibitem{TiTe2_4}Allen, P. Chetty, N. TiTe2: Inconsistency between transport properties and photoemission results. Phys. Rev. B 50, 855 (1994).
\bibitem{TiTe2_5}Di Salvo, F. J., Moncton, D. E. Waszczak, J. V. Electronic properties and superlattice formation in the semimetal TiSe2 . Phys. Rev. B 14, 4321–4328 (1976).
\bibitem{TiTe2_6}Rossnagel, K. On the origin of charge-density waves in select layered transition-metal dichalcogenides. J. Phys. Condens. Matter. 23, 213001 (2011).
\bibitem{TiTe2_7}Chen, P. et al. Dimensional Effects on the Charge Density Waves in Ultrathin Films of TiSe2 . Nano. Lett. 16, 6331–6336 (2016).
%=========================================================
%=========================================================
\bibitem{convexfreeenerg} M. Valiev, G. W. Fernando Generalized Kohn-Sham Density-Functional Theory via Effective Action Formalism // arXiv Condensed Matter, Strongly Correlated Electrons 1997 
\bibitem{Hohenberg&Khon}
Hohenberg P., Khon W.  Inhomogeneous Electron Gas // Physical Review. --- 1964, V. 136.
\bibitem{Khon&Sham}
Kohn W., L.J.Sham Self-Consistent Equations Including Exchange and Correlation Effects // Phys. Rev. – 1965. – V. 140.
\bibitem{PBE}
John P. Perdew, Kieron Burke, and Matthias Ernzerhof Generalized Gradient Approximation Made Simple // Phys. Rev. Lett. 77, 3865 – 28 October 1996;
\bibitem{K-S energy}
M. C. Payne, M. P. Teter, D. C. Allan, T. A. Arias, and J. D. Joannopoulos Iterative minimization techniques for ab initio total-energy calculations: molecular dynamics and conjugate gradients // Rev. Mod. Phys. 64, 1045 – Published 1 October 1992
\bibitem{PW91}
John P. Perdew, J. A. Chevary, S. H. Vosko, Koblar A. Jackson, Mark R. Pederson, D. J. Singh, and Carlos Fiolhais Atoms, molecules, solids, and surfaces: Applications of the generalized gradient approximation for exchange and correlation
// Phys. Rev. B 46, 6671 – 15 September 1992
\bibitem{Swapan&Gosh&Parr}
Swapan K. Ghosh and Robert G. Parr Phase-space approach to the exchange-energy functional of density-functional theory //
Phys. Rev. A 34, 785 – Published 1 August 1986
\bibitem{Becke&Roussel}
A. D. Becke and M. R. Roussel Exchange holes in inhomogeneous systems: A coordinate-space model //
Phys. Rev. A 39, 3761 – Published 1 April 1989
\bibitem{Tao&Perdew}
Jianmin Tao, John P. Perdew, Viktor N. Staroverov, and Gustavo E. Scuseria Climbing the Density Functional Ladder: Nonempirical Meta–Generalized Gradient Approximation Designed for Molecules and Solids //
Phys. Rev. Lett. 91, 146401 – Published 30 September 2003
\bibitem{SCAN}
Jianwei Sun, Adrienn Ruzsinszky, and John.P. Perdew Strongly Constrained and Appropriately Normed Semilocal Density Functional //
Phys. Rev. Lett. 115, 036402 – Published 14 July 2015
\bibitem{QMC}
W. M. C. Foulkes, L. Mitas, R. J. Needs, and G. Rajagopal Quantum Monte Carlo simulations of solids //
Rev. Mod. Phys. 73, 33 – Published 5 January 2001
\bibitem{CCSD(T)}
Krishnan Raghavachari, Gary W., Trucks John, A.Pople, Martin Head-Gordon A fifth-order perturbation comparison of electron correlation theories // Chemical Physics Letters
Volume 157, Issue 6, 26 May 1989, Pages 479-483
\bibitem{S22}
Petr Jurečka, Jiří Šponer, Jiří Černýa and Pavel Hobza Benchmark database of accurate (MP2 and CCSD(T) complete basis set limit) interaction energies of small model complexes, DNA base pairs, and amino acid pairs // Physical Chemistry Chemical Physics Issue 17, 2006



%=========================================================

\end{thebibliography}
